Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-04-26 extended_catalog/paper/extended_catalog.tex
Modifications

We use another monte carlo study to determine the Fermi LAT's sensitivity to
spatially extended sources.

@@

% * Plots we make ...

>>>>

We performed another monte carlo study to determine the Fermi LAT's
sensitivity to spatially extended sources. The sensitivity to extension
is defined as the flux at which $\text{TS}_\text{ext}$ for a source is on
average equal to 25 (for a given spectral model). We emphasize that this
is not the sensitivity to detect a source, but instead the sensitivity
to detecting a source as being extended.  One would expect that we would
become very insensitive to detecting the extension of very small sources
that look just like the PSF. Similarly, we would be very insensitive to
very large sources which would get lost in the background. Furtheremore,
one expects our sensitivity to be greater for harder sources since our
angular resolution improves with energy.

To calculate the LAT's sensitivity to spatially extended sources,
we simulated sources with a disk morphology on top of a powerlaw
Sreekumar-like spectrum.\cite{Sreekumar et al. ApJ 494 pag 523 1998}.
We calculated the sensitivity for sources of a spectral index $\gamma$
of 1.5, 2, 2.5, and 3 and for sources of 20 extensions varying
from $0.1^\circ$ to $2.0^\circ$ To calculate the sensitivity, we
found a flux for which $\text{TS}_\text{ext}<25$ and a flux for which
$\text{TS}_\text{ext}>25$ and then multiple simulations
of fluxes in the range were run. A line was fit to the 
flux vs $\text{TS}_\text{ext}$ data to determine the average
flux for which $\text{TS}_\text{ext}=25$.

The resulting Fermi sensitivity to extension is shown in figure~\ref{sensitivity_ext}.

@@
